Topological Sigma Models from Generalized Para-Complex Geometry

### 2019-11-22 draft2.tex
merge2

Suppose $M$ is a manifold with boundary, and let $\cE(M)$ denote the space of fields of a classical theory on $M$. 
For instance, $\cE(M)$ will be a mapping space of the form ${\rm Map}(M, X)$ where $X$ is shifted symplectic. 
Let $\cE(\partial M)$ denote the restriction of the fields to the boundary of $M$. 
For the mapping space example, this is simply the space of maps ${\rm Map}(\partial M, X)$.

>>>>

Suppose $M$ is a manifold with boundary, and let $\cE(M)$ denote the space of fields of a classical theory on $M$. 
For us, $\cE(M)$ will be a mapping space of the form ${\rm Map}(M, X)$ where $X$ is shifted symplectic. 
Let $\cE(\partial M)$ denote the restriction of the fields to the boundary of $M$. 
For the mapping space example, this is simply the space of maps ${\rm Map}(\partial M, X)$.

In general, when $M$ is not closed, $\cE(M)$ will not carry a $(-1)$-shifted symplectic structure.
However,
